\bf A Hierarchical Model for Heterogenous Reliability Field Data

### 2018-05-30 paper/m-lb-m-technometrics.tex
Complete small list of edits..
- change notation t_{p_i} to be consistent throughout
- add "Drive model " to plot names for clarity
- fix typos/small grammar/wording things
- add reference (Gelman 2004)
- add acknowledgment (Backblaze)
- move Appendix to Supplementary materials

\begin{abstract}
When analyzing field data on consumer products, model-based approaches to inference require a model with sufficient flexibility to account for multiple kinds of failures. The causes of failure, while not interesting to the consumer per se, can lead to various observed lifetime distributions.  Because of this, standard lifetime models, such as using a single Weibull or
lognormal distribution may be inadequate. Usually cause-of-failure information will not be available to the consumer and thus traditional competing risk analyses cannot be performed.
Furthermore, when the information carried by lifetime data are limited by sample size, censoring, and truncation, estimates can be unstable and suffer from imprecision. These limitations are typical; for example, lifetime data for high-reliability products will naturally tend to be right-censored.

@@

\section{Model for field data}
\label{sec:GLFP model}
The methods presented in this paper
could employ any of the commonly-used lifetime distributions such as
the Weibull or lognormal (see Chapters 4 and 5 of
\cite{meeker} for others) to describe either the early
(infant mortality) failures or the wearout failures. 
In this paper
we use the Weibull distribution to describe both the early and
wearout failures for the following reasons.
\begin{itemize}
\item
This combination of distributions provides a good fit to the data.
\item
Mechanistically, within both of the different kinds of failures there
are almost certainly several, if not many, different competing
causes. The actual cause for any particular failed drive
would be the minimum time of all of these potential causes, suggesting a
Weibull distribution because of extreme value theory (see page 86  of
\cite{meeker}) for further discussion of this point.
\end{itemize}

To simplify the
presentation and because it adequately describes our example data,
we will use the Weibull distribution to describe both the early and
wearout failures. Changing to any other combination of distributions
in the log-location-scale family of distributions is
straightforward.

@@

Following the suggestions given in \cite{LiMeeker2014} and Section 15.2 of \cite{intervals} we use an alternative parameterization
where the usual scale parameter $\alpha$ is replaced by the $p$ quantile $t_{p}=\alpha \left
[-\log(1-p)\right ]^{\sigma}$ (which is also a scale parameter). Replacing $\alpha$ in (1) with the
$\alpha=t_{p}/[-\log(1-p)]^{\sigma}$ gives
\begin{align*}
\nonumber
\Pr(T \leq t|t_{p},\sigma ) = F(t|t_{p},\sigma)&=1-
\exp \left [-\left (\frac{t}{t_{p}/[-\log(1-p)]^{\sigma}} \right )^{1/ \sigma}
\right ]\\
\label{equation:reparameterized.weibull.cdf}
&=1 - \exp\left[\log(1-p)\left(\frac{t}{t_{p}}\right)^{1/\sigma}\right], \quad t > 0
\end{align*}
There are three important reasons for using this parameterization.
\begin{itemize}
\item
Especially with a high-reliability product, it will be easier to
elicit prior information about a quantile  ($t_p$) in the lower tail of the
distribution than it will be to elicit prior information about
$\alpha$ (approximately the $0.63$ quantile). In addition, there is generally available
information about the shape parameter, $\sigma$, for a given failure
mechanism (e.g., if the failure is due to a wearout mechanism, then
it is known that $\sigma<1$). 
\item
Because of heavy censoring in reliability field data, the parameter
estimates of the $\mu$ and $\sigma$ parameters will generally be
highly correlated and thus specification of independent marginal
prior distributions would be be inappropriate. On the other hand,
estimates of $t_{p}$ and $\sigma$, for some appropriately chosen
value of $p$, will be approximately independent, allowing the easier
elicitation and specification of independent marginal prior
distributions. For example, if a typical field data set has 10\% of units
failing, then choosing $t_{0.05}$ would 
work well.
\item Bayesian MCMC estimation will be better behaved due to reduced correlation between $t_p$ and $\sigma$ (relative to $\alpha$ and $\sigma$).
\end{itemize}

\subsection{Generalized Limited Failure Population model}
\label{subsec:GLFP model}
Let $F_1,F_2$ be Weibull distributions with parameters $(t_{p1},\sigma_1)$ and $(t_{p2}, \sigma_2)$, respectively.
The Generalized Limited Failure Population model (GLFP) of \citet{chan} is defined as follows: Let $T \sim \op{GLFP}(\pi, t_{p1},\sigma_1,t_{p2},\sigma_2)$ Then
$$\Pr(T \le t) = H(t) = 1 - (1-\pi\, F_{1}(t))(1 - F_{2}(t)),\, t>0,\, 0 < \pi < 1.$$

@@

Taking the derivative of the (marginal) cdf, the density for the GLFP model is
\begin{align*}
h(t|\pi, t_{p1},\sigma_1, t_{p2}, \sigma_2) = \pi & f_1(t|t_{p1},\sigma_1)\left(1-F_2(t|t_{p2},\sigma_2)\right) + \\ & f_2(t|t_{p2},\sigma_2)\left(1-\pi F_1(t|t_{p1},\sigma_1\right).
\end{align*}

@@

\subsection{Likelihood}
\label{subsec:likehood}
We now give the general form for the likelihood function, taking into account left truncation and right censoring.  Let $t_{i}$ denote the end of the observed lifetime of unit $i$, in hours.  Let $t_i^L$ be the left truncation time, the age of unit $i$ when data reporting commenced. Additionally, let $c_i$ be an indicator for censoring; $c_i=1$ if the failure time is right-censored, $c_1=0$ if the unit failed (at time $t_i$). The likelihood for the GLFP is a function of the parameters $\bm{\theta} = (\pi,t_{p1}, \sigma_1, t_{p2}, \sigma_2)$.  Assuming the lifetimes of all units are independent, the likelihood for the data, $t_1,\ldots,t_n$ is
\begin{equation}
\label{equation:likelihood}
L(\bm{\theta})= \prod_{i=1}^{n} \left[\frac{h(t_i;\bm{\theta})}{1-H(t_i^L;\bm{\theta})}\right]^{1-c_i} \left[ \frac{1-H(t_i;\bm{\theta})}{1-H(t_i^L;\bm{\theta})} \right]^{c_i}
\end{equation}

@@

\subsection{Analysis of a single drive-model}
\label{subsec:ex1}
To illustrate the GLFP model, we will present an analysis of the drive-model with the most observed failures, Drive-model 14.  The Kaplan-Meier (K-M) estimate plotted below suggests at least two failure modes.  The curve has a slow ramp up in failures until about 10,000 hours (early failures), and increases more rapidly from about 10,000 to 20,000 hours (presumably wearout failures).  Besides our empirical observation, it is well known that computer hard drives have a mixture of early and late failures \citep{chan}.  Therefore, there is both an empirical and a theoretical justification to use the GLFP model in this application.

@@

To estimate the parameters of the GLFP model we use a Bayesian approach, selecting proper, but generally diffuse, prior distributions to improve identification of the model parameters. Having a proper prior distribution also ensures a proper posterior distribution. We reparameterize the component Weibull distributions using the $0.50$ quantile for the early failure mode ($t_{0.5,1}$) and the $0.20$ quantile for the wearout failure mode ($t_{0.2,2}$). \\

When eliciting prior distribution information it is much easier to ask about recognizable characteristics of a distribution instead of the traditional parameters of the distribution.  Following the approach used in \cite[Section 15.2.2]{intervals} we will use diagonal braces ($\langle.,.\rangle$) to refer to $95$ percent central probability intervals, rather than the standard model parameters when specifying prior distributions (See the Supplementary Material for standard density plots of the priors).  Using this convention the prior distributions used in our analyses are
%$$t_{0.5,1} \sim \op{Lognormal}(8,4), \quad t_{0.2,2} \sim \op{Lognormal}(10,4)$$
$$t_{0.5,1} \sim \op{Lognormal} \langle 1.7,\,7.6\times 10^6 \rangle,\quad
t_{0.2,2} \sim \op{Lognormal}\langle 8.6, \, 5.6\times 10^7 \rangle$$
$$\pi \sim \op{Logit-normal}\langle 0.001,\, 0.71 \rangle,\quad
\sigma_1, \sigma_2 \stackrel{ind.}{\sim} \op{Lognormal}\langle 0.0074 ,\,130 \rangle. $$
%\quad \sigma_2 \sim \op{Lognormal}\langle 7.4 \times 10 ^{-3} ,1.3 \times 10^2  \rangle $$

@@

\begin{table}[H]
\centering
\begin{tabular}{lrrr}
  \hline
 & Lower & Estimate & Upper \\ 
  \hline
$\pi$ & 0.033 & 0.054 & 0.099 \\ 
 $\beta_1 = 1/\sigma_1 $ & 0.47 & 1.13 & 1.72 \\ 
  $\beta_2 = 1/\sigma_2$ & 4.47 & 4.70 & 4.95 \\ 
  $t_{0.5,1}$ & $1.03$  & $2.28$ & $3.99$\\ 
  $t_{0.2,2}$ & $18.0$ & $18.2$ & $18.6$ \\ 
   \hline
\end{tabular}
\caption{\footnotesize Posterior 95\% Credible Intervals for the 5 GLFP parameters for Drive-model 14.  The quantiles are in thousands of hours.}
\label{table:1}
\end{table}

Probability plotting is a simple method to assess and compare the adequacy of members of the log-location-scale family of distributions.  After properly transforming the axes of a plot, graphing an empirical estimate of fraction failing as a function of time along with confidence bands provides a visual assessment of distributional goodness of fit.  We applied this method using the Kaplan-Meier nonparametric estimate of the empirical cdf.  With left truncation, however, the standard Kaplan-Meier estimator is biased, so we used an adjusted version due to \citet[Chapter 11]{meeker} (see Appendix for a detailed description).

In Figure \ref{ex1-overlay}, we overlay the posterior median of the fitted GLFP model onto the adjusted K-M estimate with axes on the Weibull probability scale.  The plot also contains 90\% pointwise credible bands associated with each estimate. While the Weibull model is inadequate for these data, the GLFP model fits quite well, as it is able to adequately describe the rapid increase in the empirical cdf between 8000 and 20,000 hours. %The discrepancy around 30,000 suggests that the GLFP may overestimate the proportion failing in the far right tail of the distribution.  While this discrepancy may appear troubling, we suggest that the right tail is of less importance for electronic goods due to obsolescence.

@@

\section{Hierarchical GLFP model}
\label{sec:Hierarchical GLFP model}
In order to describe an entire product population, consisting of different but similar sub-populations, and because of the limited amount of data from many of the sub-populations, we model sub-population-specific parameters hierarchically, borrowing strength across sub-populations.

@@

In a hierarchical model, the parameters are modeled as random variables, varying across different sub-populations.  For example
\begin{equation*}
\sigma_{1g} \ind \op{Lognormal} \left( \eta_{\sigma_1}, \tau^2_{\sigma_1} \right)
\end{equation*}
\begin{equation*}
\sigma_{2g} \ind \op{Lognormal} \left( \eta_{\sigma_2}, \tau^2_{\sigma_2}\right)\op{Tr}\left(0, 1\right)
\end{equation*}
\begin{equation}
\label{eq:hier-model}
t_{p_{1}g} = \exp\left(\mu_{1g} + \sigma_{1g}\,\Phi^{-1}(p_1)\right)  \ind \op{Lognormal} \left(\eta_{t_{p_1}}, \tau^2_{t_{p_1}}\right)
\end{equation}
\begin{equation*}
t_{p_{2}g} = \exp\left(\mu_{2g} + \sigma_{2g}\,\Phi^{-1}(p_2)\right)  \ind \op{Lognormal} \left(\eta_{t_{p_2}}, \tau^2_{t_{p_2}}\right)
\end{equation*}
\begin{equation*}
\pi_g \ind \op{Logit-normal}(\eta_\pi, \tau^2_\pi).
\end{equation*}

@@

\begin{align*}
\mbox{lpd} &= \sum_{g=1}^G \sum_{i=1}^{n_g} \log[p(t_{new,g,i}|t, t^L, c)] \\
&= \sum_{g=1}^G \sum_{i=1}^{n_g} \log \left[ \int p(t_{new,g, i}|\theta) p(\theta|t,t^L,c) d\theta \right].
\end{align*}
\noindent Using this criterion, we should choose the model with the highest expected lpd (elpd) for a new data set $\{t_{new,g,i}:g=1,\ldots,G; i=1,\ldots,n_g\}$. Notationally suppressing the conditioning on $t^L$ and $c$,
\begin{equation}
\mbox{elpd} = \op{E}_h \mbox{lpd} = \sum_{g=1}^G \sum_{i=1}^{n_g} \int \log [p(t_{new, g, i}|t)] h(t_{new,g,i}) d t_{new,g,i}
\label{elpd}
\end{equation}
where $h$ is a density for the true distribution of $t_{new,g,i}$. Although $h$ is unknown, leave-one-out cross-validation provides a robust estimator:
\begin{equation}
\widehat{\text{elpd}} = \sum_{g=1}^G \sum_{i=1}^{n_g} \log [p(t_{g,i}|t_{-(g,i)})].
\label{loo-est}
\end{equation}
The \texttt{R} package, \texttt{loo} \citep{loo}, computes an approximation of (\ref{loo-est}) provided that the observations $t_i$ are conditionally independent. It employs an importance sampling method that uses $S$ saved MCMC draws to compute smoothed importance weights, $w_{i,s}$, approximating $p(t_{g,i}|t_{-(g,i)})$ with $\sum_{s=1}^S w_{i,s} p(t_{g,i})/\sum_{s=1}^S w_{i,s}$. In addition to providing an estimate of (\ref{elpd}), their method also produces a standard error based on an asymptotic result.  A measure of the effective number of parameters is also available using the sum of the posterior variance of the log predictive density for each observation.
%When $n$ is large, the distribution of the elpd is approximately normal and different models can be compared statistically. 
% To statistically compare the GLFP Models, we estimated the predictive accuracy of the 4 different models using an approximate leave-one-out cross validation (LOO) method.  As outlined in Vehtari et. al, the predictive accuracy from a fitted Bayesian model can be estimated simply with posterior draws of the model parameters rather than re-fitting the model with different data sets \cite{vehtari}.  For each observation, $i$, the log point-wise predictive density is calculated over the full set of posterior samples with data point $i$ removed.  
% The final expected log point-wise predictive density (elpd) is the sum over all observations (elpd $=\sum{\log p(y_i|y_{-i})}$).

@@

\paragraph{Model 2} $t_{p_{2}g}$ varies by drive-model. To help with model identifiably, we tighten the priors on the early failure mode:
$$ \pi \sim \op{Logit-normal}\langle 0.007,\, 0.26 \rangle,$$
$$\sigma_1 \sim \op{Lognormal}\langle 0.14,\, 7.1\rangle,$$ 
$$t_{0.5} \sim \op{Lognormal} \langle 22,\, 5.5 \times 10^{4} \rangle.$$

@@

Where applicable, prior distributions on hyperparameters are as listed below. We use half-Cauchy prior distributions on hierarchical scale parameters. As for the location hyperparameters, we choose weakly informative prior distributions centered around the corresponding prior mean for the non-hierarchical model.
$$\eta_{\pi} \sim \op{Normal}(-3, 1^2),\quad \tau_{\pi} \sim \op{Half-Cauchy}(0, 1)$$
$$\eta_{\sigma_2}  \sim \op{Normal}(0, 2^2),\quad
\tau_{\sigma_2}  \sim \op{Half-Cauchy}(0, 1)$$
$$\eta_{t_{0.2}}  \sim \op{Normal}(9, 2^2),\quad
\tau_{t_{0.2}}  \sim \op{Half-Cauchy}(0, 1).$$

@@

\begin{figure}
\begin{table}[H]
\centering
\begin{tabular}{rrrrrrrr}
  \hline
 & $\widehat{\text{elpd}}$ \ & \thead{Estimated Difference \\ in $\widehat{\text{elpd}}$} \ & \thead{Standard Error of \\ the Difference} & \thead{Effective Number of \\ Parameters}\\ 
  \hline
Model 4 & -13309.5 & 40.7 & 11.3 & 92.5 \\ 
Model 3 & -13350.2 & 458.8 & 31.0 & 68.8 \\ 
Model 2 & -13809.0 & 3674.6 & 96.2 & 49.6 \\ 
Model 1 & -17483.6 &  &  & 4.3 \\
   \hline
\end{tabular}
\caption{\footnotesize Expected log pointwise predictive density (elpd) and related statistics for each model.}
\label{table:2}
\end{table}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{ppcheck-sample}
\caption{\footnotesize Adjusted K-M estimates of the proportion failing for a representative subset of drive-models. Both the original data (\textbf{bold} line) and 19 ``replicated" data sets from the posterior predictive distribution (\textit{dashed} lines) are shown.}
\label{fig:post-pred-KM}
\end{figure}

@@

Figure 8 shows a similar pair of plots for Drive-model 43. The data for this Drive-model are heavily truncated; the observed units had run for quite some time before data were made available with the earliest left-truncation time at 12,189 hours. In the bottom half of Figure \ref{fig:ex-mod-43} we contrast the posterior median for drive-model 43 to an average GLFP cdf for the entire population, which we call the ``global average" cdf; a description of the global average cdf is given in Appendix \ref{global-avg}. We can see that the lack of data for this drive-model during early life results in a diffuse posterior centered around the global average cdf until about 10,000 hours when they diverge. Although the posterior is close to the adjusted K-M, it has been shrunk toward the global average cdf.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=.8\textwidth]{dm-eval}
  \caption{\footnotesize Left: 90\% CI of the posterior predictive distributions for $e^{-0.4 t_{g,new}}$ the depreciated value at failure (VAF) for a new unit for each Drive-model.
  Right: A comparison (90\% CI) of the predictive distribution of TTF in hundreds of thousands of hours (top) and VAF (bottom) based on 40\% depreciation for the best 11 drive-models, shows that rankings produced by the two measures are not equivalent.}
  \label{fig5}
\end{figure}

@@

\item[Model code and plots] Stan code for Model 4 as well as the complete set of plots similar to Figures 5 and 6 (supplementary.pdf)

>>>>

\begin{abstract}
When analyzing field data on consumer products, model-based approaches to inference require a model with sufficient flexibility to account for multiple kinds of failures. The causes of failure, while not interesting to the consumer per se, can lead to various observed lifetime distributions.  Because of this, standard lifetime models, such as using a single Weibull or
lognormal distribution, may be inadequate. Usually cause-of-failure information will not be available to the consumer and thus traditional competing risk analyses cannot be performed.
Furthermore, when the information carried by lifetime data are limited by sample size, censoring, and truncation, estimates can be unstable and suffer from imprecision. These limitations are typical; for example, lifetime data for high-reliability products will naturally tend to be right-censored.

@@

\section{Model for field data}
\label{sec:GLFP model}
The methods presented in this paper
could employ any of the commonly-used lifetime distributions such as
the Weibull or lognormal (see Chapters 4 and 5 of
\cite{meeker} for others) to describe either the early
(infant mortality) failures or the wearout failures. 
In this paper
we use the Weibull distribution to describe both the early and
wearout failures for the following reasons.
\begin{itemize}
\item
This combination of distributions provides a good fit to the data.
\item
Mechanistically, within both of the different kinds of failures there
are almost certainly several, if not many, different competing
causes. The actual cause for any particular failed drive
would be the minimum time of all of these potential causes, suggesting a
Weibull distribution because of extreme value theory (see page 86  of
\cite{meeker} for further discussion of this point.)
\end{itemize}

%To simplify the presentation and because it adequately describes our example data, we will use the Weibull distribution to describe both the early and wearout failures.

Changing to any other combination of distributions
in the log-location-scale family of distributions is
straightforward.

@@

Following the suggestions given in \cite{LiMeeker2014} and Section 15.2 of \cite{intervals} we use an alternative parameterization
where the usual scale parameter $\alpha$ is replaced by the $p$ quantile $t_{p}=\alpha \left
[-\log(1-p)\right ]^{\sigma}$ (which is also a scale parameter). Replacing $\alpha$ in (1) with the
$\alpha=t_{p}/[-\log(1-p)]^{\sigma}$ gives
\begin{align*}
\nonumber
\Pr(T \leq t|t_{p},\sigma ) = F(t|t_{p},\sigma)&=1-
\exp \left [-\left (\frac{t}{t_{p}/[-\log(1-p)]^{\sigma}} \right )^{1/ \sigma}
\right ]\\
\label{equation:reparameterized.weibull.cdf}
&=1 - \exp\left[\log(1-p)\left(\frac{t}{t_{p}}\right)^{1/\sigma}\right], \quad t > 0
\end{align*}
There are three important reasons for using this parameterization.
\begin{itemize}
\item
Especially with a high-reliability product, it will be easier to
elicit prior information about a quantile  ($t_p$) in the lower tail of the
distribution than it will be to elicit prior information about
$\alpha$ (approximately the $0.63$ quantile). In addition, there is generally available
information about the shape parameter, $\sigma$, for a given failure
mechanism (e.g., if the failure is due to a wearout mechanism, then
it is known that $\sigma<1$). 
\item
Because of heavy censoring in reliability field data, the parameter
estimates of the $\mu$ and $\sigma$ parameters will generally be
highly correlated and thus specification of independent marginal
prior distributions would be be inappropriate. On the other hand,
estimates of $t_{p}$ and $\sigma$, for some appropriately chosen
value of $p$, will be approximately independent, allowing the easier
elicitation and specification of independent marginal prior
distributions. For example, if a typical field data set has 10\% of units
failing, then choosing $t_{0.05}$ would 
work well.
\item Bayesian MCMC estimation will be better behaved due to reduced correlation between $t_p$ and $\sigma$ (relative to $\alpha$ and $\sigma$).
\end{itemize}
 \cite{gelman2004parameterization} provides a more general discussion of reparameterization and Bayesian inference.

\subsection{Generalized Limited Failure Population model}
\label{subsec:GLFP model}
Let $F_1,F_2$ be Weibull distributions with parameters $(t_{p_1},\sigma_1)$ and $(t_{p_2}, \sigma_2)$, respectively.
The Generalized Limited Failure Population model (GLFP) of \citet{chan} is defined as follows: Let $T \sim \op{GLFP}(\pi, t_{p_1},\sigma_1,t_{p_2},\sigma_2)$ Then
$$\Pr(T \le t) = H(t) = 1 - (1-\pi\, F_{1}(t))(1 - F_{2}(t)),\, t>0,\, 0 < \pi < 1.$$

@@

Taking the derivative of the (marginal) cdf, the density for the GLFP model is
\begin{align*}
h(t|\pi, t_{p_1},\sigma_1, t_{p_2}, \sigma_2) = \pi & f_1(t|t_{p_1},\sigma_1)\left(1-F_2(t|t_{p_2},\sigma_2)\right) + \\ & f_2(t|t_{p_2},\sigma_2)\left(1-\pi F_1(t|t_{p_1},\sigma_1\right).
\end{align*}

@@

\subsection{Likelihood}
\label{subsec:likehood}
We now give the general form for the likelihood function, taking into account left truncation and right censoring.  Let $t_{i}$ denote the end of the observed lifetime of unit $i$, in hours.  Let $t_i^L$ be the left truncation time, the age of unit $i$ when data reporting commenced. Additionally, let $c_i$ be an indicator for censoring; $c_i=1$ if the failure time is right-censored, $c_1=0$ if the unit failed (at time $t_i$). The likelihood for the GLFP is a function of the parameters $\bm{\theta} = (\pi,t_{p_1}, \sigma_1, t_{p_2}, \sigma_2)$.  Assuming the lifetimes of all units are independent, the likelihood for the data, $t_1,\ldots,t_n$ is
\begin{equation}
\label{equation:likelihood}
L(\bm{\theta})= \prod_{i=1}^{n} \left[\frac{h(t_i;\bm{\theta})}{1-H(t_i^L;\bm{\theta})}\right]^{1-c_i} \left[ \frac{1-H(t_i;\bm{\theta})}{1-H(t_i^L;\bm{\theta})} \right]^{c_i}
\end{equation}

@@

\subsection{Analysis of a single drive-model}
\label{subsec:ex1}
To illustrate the GLFP model, we will first present an analysis of the drive-model with the most observed failures, Drive-model 14.  The Kaplan-Meier (K-M) estimate plotted below suggests at least two failure modes.  The curve has a slow ramp up in failures until about 10,000 hours (early failures), and increases more rapidly from about 10,000 to 20,000 hours (presumably wearout failures).  Besides our empirical observation, it is well known that computer hard drives have a mixture of early and late failures \citep{chan}.  Therefore, there is both an empirical and a theoretical justification to use the GLFP model in this application.

@@

To estimate the parameters of the GLFP model we use a Bayesian approach, selecting proper, but generally diffuse, prior distributions to improve identification of the model parameters. Having a proper prior distribution also ensures a proper posterior distribution. We reparameterize the component Weibull distributions using the $0.50$ quantile for the early failure mode ($t_{p_1=0.5}$) and the $0.20$ quantile for the wearout failure mode ($t_{p_2=0.2}$). \\

When eliciting prior distribution information it is much easier to ask about recognizable characteristics of a distribution instead of the traditional parameters of the distribution.  Following the approach used in \cite[Section 15.2.2]{intervals} we will use diagonal braces ($\langle.,.\rangle$) to refer to $95$ percent central probability intervals, rather than the standard model parameters when specifying prior distributions (See the Supplementary Material for standard density plots of the priors).  Using this convention the prior distributions used in our analyses are
%$$t_{0.5,1} \sim \op{Lognormal}(8,4), \quad t_{0.2,2} \sim \op{Lognormal}(10,4)$$
$$t_{p_1} \sim \op{Lognormal} \langle 1.7,\,7.6\times 10^6 \rangle,\quad
t_{p_2} \sim \op{Lognormal}\langle 8.6, \, 5.6\times 10^7 \rangle$$
$$\pi \sim \op{Logit-normal}\langle 0.001,\, 0.71 \rangle,\quad
\sigma_1, \sigma_2 \stackrel{ind.}{\sim} \op{Lognormal}\langle 0.0074 ,\,130 \rangle$$
where $p_1=0.2$ and $p_2=0.5$.
%\quad \sigma_2 \sim \op{Lognormal}\langle 7.4 \times 10 ^{-3} ,1.3 \times 10^2  \rangle $$

@@

\begin{table}[H]
\centering
\begin{tabular}{lrrr}
  \hline
 & Lower & Estimate & Upper \\ 
  \hline
$\pi$ & 0.033 & 0.054 & 0.099 \\ 
 $\beta_1 = 1/\sigma_1 $ & 0.47 & 1.13 & 1.72 \\ 
  $\beta_2 = 1/\sigma_2$ & 4.47 & 4.70 & 4.95 \\ 
  $t_{p_1=0.5}$ & $1.03$  & $2.28$ & $3.99$\\ 
  $t_{p_2=0.2}$ & $18.0$ & $18.2$ & $18.6$ \\ 
   \hline
\end{tabular}
\caption{\footnotesize Posterior 95\% Credible Intervals for the 5 GLFP parameters for Drive-model 14.  The quantiles are in thousands of hours.}
\label{table:1}
\end{table}

Probability plotting is a simple method to assess and compare the adequacy of members of the log-location-scale family of distributions.  After properly transforming the axes of a plot, graphing an empirical estimate of fraction failing as a function of time along with confidence bands provides a visual assessment of distributional goodness of fit.  We applied this method using the Kaplan-Meier nonparametric estimate of the empirical cdf.  With left truncation, however, the standard Kaplan-Meier estimator is biased, so we used an adjusted version due to \citet[Chapter 11]{meeker} (details are given in Appendix A in the Supplementary Materials).

In Figure \ref{ex1-overlay}, we overlay the posterior median of the fitted GLFP model onto the adjusted K-M estimate with axes on the Weibull probability scale.  The plot also contains 90\% pointwise credible bands associated with each estimate. While a single Weibull distribution is inadequate to describe these data, the GLFP model fits quite well, as it is able to adequately describe the rapid increase in the empirical cdf between 8000 and 20,000 hours. %The discrepancy around 30,000 suggests that the GLFP may overestimate the proportion failing in the far right tail of the distribution.  While this discrepancy may appear troubling, we suggest that the right tail is of less importance for electronic goods due to obsolescence.

@@

\section{Hierarchical GLFP model}
\label{sec:Hierarchical GLFP model}
In order to describe an entire product population consisting of different but similar sub-populations, and because of the limited amount of data from many of the sub-populations, we model sub-population-specific parameters hierarchically, borrowing strength across sub-populations.

@@

In a hierarchical model, the parameters are modeled as random variables, varying across different sub-populations.  Although other distributions might be specified in general, for the Backblaze example, we used
\begin{equation*}
\sigma_{1g} \ind \op{Lognormal} \left( \eta_{\sigma_1}, \tau^2_{\sigma_1} \right)
\end{equation*}
\begin{equation*}
\sigma_{2g} \ind \op{Lognormal} \left( \eta_{\sigma_2}, \tau^2_{\sigma_2}\right)\op{Tr}\left(0, 1\right)
\end{equation*}
\begin{equation}
\label{eq:hier-model}
t_{p_{1}g} = \exp\left(\mu_{1g} + \sigma_{1g}\,\Phi^{-1}(p_1)\right)  \ind \op{Lognormal} \left(\eta_{t_{p_1}}, \tau^2_{t_{p_1}}\right)
\end{equation}
\begin{equation*}
t_{p_{2}g} = \exp\left(\mu_{2g} + \sigma_{2g}\,\Phi^{-1}(p_2)\right)  \ind \op{Lognormal} \left(\eta_{t_{p_2}}, \tau^2_{t_{p_2}}\right)
\end{equation*}
\begin{equation*}
\pi_g \ind \op{Logit-normal}(\eta_\pi, \tau^2_\pi).
\end{equation*}

@@

\begin{align*}
\mbox{lpd} &= \sum_{g=1}^G \sum_{i=1}^{n_g} \log[p(t_{new,g,i}|t, t^L, c)] \\
&= \sum_{g=1}^G \sum_{i=1}^{n_g} \log \left[ \int p(t_{new,g, i}|\theta) p(\theta|t,t^L,c) d\theta \right].
\end{align*}
\noindent Using this criterion, we should choose the model with the highest expected lpd (elpd) for a new data set $\{t_{new,g,i}:g=1,\ldots,G; i=1,\ldots,n_g\}$. Notationally suppressing the conditioning on $t^L$ and $c$,
\begin{equation}
\mbox{elpd} = \op{E}_h (\mbox{lpd}) = \sum_{g=1}^G \sum_{i=1}^{n_g} \int \log [p(t_{new, g, i}|t)] h(t_{new,g,i}) d t_{new,g,i}
\label{elpd}
\end{equation}
where $h$ is a density for the true distribution of $t_{new,g,i}$. Although $h$ is unknown, leave-one-out cross-validation provides a robust estimator:
\begin{equation}
\widehat{\text{elpd}} = \sum_{g=1}^G \sum_{i=1}^{n_g} \log [p(t_{g,i}|t_{-(g,i)})].
\label{loo-est}
\end{equation}
The \texttt{R} package, \texttt{loo} \citep{loo}, computes an approximation of (\ref{loo-est}) provided that the observations $t_i$ are conditionally independent. It employs an importance sampling method that uses $S$ saved MCMC draws to compute smoothed importance weights, $w_{i,s}$, approximating $p(t_{g,i}|t_{-(g,i)})$ with $\sum_{s=1}^S w_{i,s} p(t_{g,i})/\sum_{s=1}^S w_{i,s}$. In addition to providing an estimate of (\ref{elpd}), their method also produces a standard error based on an asymptotic result.  A measure of the effective number of parameters is also available using the sum of the posterior variance of the log predictive density for each observation.
%When $n$ is large, the distribution of the elpd is approximately normal and different models can be compared statistically. 
% To statistically compare the GLFP Models, we estimated the predictive accuracy of the 4 different models using an approximate leave-one-out cross validation (LOO) method.  As outlined in Vehtari et. al, the predictive accuracy from a fitted Bayesian model can be estimated simply with posterior draws of the model parameters rather than re-fitting the model with different data sets \cite{vehtari}.  For each observation, $i$, the log point-wise predictive density is calculated over the full set of posterior samples with data point $i$ removed.  
% The final expected log point-wise predictive density (elpd) is the sum over all observations (elpd $=\sum{\log p(y_i|y_{-i})}$).

@@

\paragraph{Model 2} $t_{p_{2}g}$ varies by drive-model. To help with model identifiably, we tighten the priors on the early failure mode:
$$ \pi \sim \op{Logit-normal}\langle 0.007,\, 0.26 \rangle,$$
$$\sigma_1 \sim \op{Lognormal}\langle 0.14,\, 7.1\rangle,$$ 
$$t_{p_1} \sim \op{Lognormal} \langle 22,\, 5.5 \times 10^{4} \rangle.$$
where $p_{1}=0.5$.

@@

Where applicable, prior distributions on hyperparameters are as listed below. We use half-Cauchy prior distributions on hierarchical scale parameters. As for the location hyperparameters, we choose weakly informative prior distributions centered around the corresponding prior mean for the non-hierarchical model.
$$\eta_{\pi} \sim \op{Normal}(-3, 1^2),\quad \tau_{\pi} \sim \op{Half-Cauchy}(0, 1)$$
$$\eta_{\sigma_2}  \sim \op{Normal}(0, 2^2),\quad
\tau_{\sigma_2}  \sim \op{Half-Cauchy}(0, 1)$$
$$\eta_{t_{p_2}}  \sim \op{Normal}(9, 2^2),\quad
\tau_{t_{p_2}}  \sim \op{Half-Cauchy}(0, 1)$$
where$p_{2}=0.2$.

@@

\begin{figure}
\begin{table}[H]
\centering
\begin{tabular}{rrccc}
  \hline
 & $\widehat{\text{elpd}}$ \ & \thead{Estimated Difference \\ in $\widehat{\text{elpd}}$} \ & \thead{Standard Error of \\ the Difference} & \thead{Effective Number of \\ Parameters}\\ 
  \hline
Model 4 & $-13{,}309.5$ & 40.7 & 11.3 & 92.5 \\ 
Model 3 & -13{,}350.2 & 458.8 & 31.0 & 68.8 \\ 
Model 2 & -13{,}809.0 & 3674.6 & 96.2 & 49.6 \\ 
Model 1 & -17{,}483.6 &  &  & 4.3 \\
   \hline
\end{tabular}
\caption{\footnotesize Expected log pointwise predictive density (elpd) and related statistics for each model.}
\label{table:2}
\end{table}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{ppcheck-sample-v2}
\caption{\footnotesize Adjusted K-M estimates of the proportion failing for a representative subset of drive-models. Both the original data (\textbf{bold} line) and 19 ``replicated" data sets from the posterior predictive distribution (\textit{dashed} lines) are shown.}
\label{fig:post-pred-KM}
\end{figure}

@@

Figure 8 shows a similar pair of plots for Drive-model 43. The data for this Drive-model are heavily truncated; the observed units had run for quite some time before data were made available with the earliest left-truncation time at 12,189 hours. In the bottom half of Figure \ref{fig:ex-mod-43} we contrast the posterior median for drive-model 43 to an average GLFP cdf for the entire population, which we call the ``global average" cdf; a description of the global average cdf is given in Appendix B in the Supplementary Materials. We can see that the lack of data for this drive-model during early life results in a diffuse posterior centered around the global average cdf until about 10,000 hours when they diverge. Although the posterior is close to the adjusted K-M, it has been shrunk toward the global average cdf.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=.8\textwidth]{dm-eval}
  \caption{\footnotesize Left: 90\% CI of the posterior predictive distributions for $e^{-0.4 t_{g,new}}$ the depreciated value at failure (VAF) for a new unit for each Drive-model.
  Right: A comparison (90\% CI) of the predictive distribution of TTF in thousands of hours (top) and VAF (bottom) based on 40\% depreciation for the best 11 drive-models, shows that rankings produced by the two measures are not equivalent.}
  \label{fig5}
\end{figure}

@@

\item[Appendices, stan model code and plots] Description of truncation adjustment to Kaplan Meier estimator, global average, Stan code for Model 4 as well as the complete set of plots similar to Figures 5 and 6 (supplementary.pdf)
